EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-06 draft.tex
Tables for experiment 1

We present the results of the experiments in this section.
% The effect of a
% different number of populations on execution time is reported in  Section
% \ref{sec:exp1results}.
% The results of the performance comparison between homogeneous and
% heterogeneous search strategies are presented in Section \ref{sec:exp2results}.     
%
\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required, in seconds, to complete an instance of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}
%
%
% \subsection{Experiment 1}
% \label{sec:exp1results}
%
with results summarized in Figure \ref{fig:spworker}.  The
experiment consisted of executing the same benchmark on EvoSwarm twice but
changing the number of populations used in each run. This is mainly
intended as a showcase of the flexibility of the tool presented in
this paper, but we also wanted to test how the number of workers
affected the time needed to reach a solution. Adding more populations
might add more overhead, so this might have a noticeable effect.
The left column in that figure has the
results when using five populations, and the right side shows the results for
ten. In principle the main issue is how to find the right number of
workers for a particular problem, but in general we wanted to check
the communication overhead when the size of the problem increases and
how the presented framework reacted to it. % Added some explanation
% here - JJ

>>>>

We present the results of the experiments in this section.
% The effect of a
% different number of populations on execution time is reported in  Section
% \ref{sec:exp1results}.
% The results of the performance comparison between homogeneous and
% heterogeneous search strategies are presented in Section \ref{sec:exp2results}.     
%

\begin{table}[]
    \caption{Speedup by worker and dimension, taking one worker as the baseline.}
    \label{tab:speedup-table}
    \vspace{0.25cm}
    \centering

    \begin{tabular}{c|r|r|r|r|r|r|}
    \cline{2-7}
    \multicolumn{1}{l|}{}           & \multicolumn{3}{c|}{5 Populations}                                          & \multicolumn{3}{c|}{10 Populations}                                         \\ \hline
    \multicolumn{1}{|l|}{Dimension} & \multicolumn{1}{c|}{2W} & \multicolumn{1}{c|}{4W} & \multicolumn{1}{c|}{8W} & \multicolumn{1}{c|}{2W} & \multicolumn{1}{c|}{4W} & \multicolumn{1}{c|}{8W} \\ \hline
    \multicolumn{1}{|c|}{2}         & 1.94                    & 3.12                    & 3.86                    & 1.84                    & 3.38                    & 5.98                    \\ \hline
    \multicolumn{1}{|c|}{3}         & 1.93                    & 2.77                    & 3.15                    & 1.90                    & 3.26                    & 5.96                    \\ \hline
    \multicolumn{1}{|c|}{5}         & 1.91                    & 2.90                    & 3.09                    & 1.91                    & 3.46                    & 6.14                    \\ \hline
    \multicolumn{1}{|c|}{10}        & 1.92                    & 3.03                    & 3.30                    & 1.90                    & 3.61                    & 6.41                    \\ \hline
    \multicolumn{1}{|c|}{20}        & 1.91                    & 3.14                    & 3.27                    & 1.89                    & 3.73                    & 6.71                    \\ \hline
    \multicolumn{1}{|c|}{40}        & 2.00                    & 2.92                    & 3.12                    & 1.95                    & 3.80                    & 7.52                    \\ \hline
    \end{tabular}
\end{table}

\begin{table}[]
    \small
    \caption{ Median of evaluation rate per second, for each number of workers and dimension}
    \label{tab:medians}
    \vspace{0.25cm}
    \centering

    \begin{tabular}{ccrr}
    \hline
               &         & 5 Populations    & 10 Populations \\
     Dimension & Workers & Median of rate & Median of rate  \\
    \hline
    2         & 1w      & 10,815.95      & 10,771.30      \\

              & 2w      & 20,704.11      & 19,197.58      \\
              & 4w      & 32,563.61      & 35,248.83      \\
              & 8w      & 40,106.09      & 59,744.88      \\
    \hline
    3         & 1w      & 9,599.62       & 9,389.69       \\
              & 2w      & 18,634.43      & 18,064.24      \\
              & 4w      & 27,607.12      & 30,419.51      \\
              & 8w      & 30,189.27      & 56,102.75      \\
    \hline
    5         & 1w      & 9,473.63       & 8,671.92       \\
              & 2w      & 18,181.18      & 16,753.68      \\
              & 4w      & 27,351.11      & 31,145.09      \\
              & 8w      & 29,257.72      & 52,985.83      \\
    \hline
    10        & 1w      & 8,353.71       & 8,145.61       \\
              & 2w      & 15,957.87      & 15,577.79      \\
              & 4w      & 25,696.70      & 29,176.94      \\
              & 8w      & 28,571.52      & 54,348.60      \\
    \hline
    20        & 1w      & 6,920.57       & 6,723.48       \\
              & 2w      & 13,297.58      & 13,136.11      \\
              & 4w      & 22,307.73      & 25,271.93      \\
              & 8w      & 24,179.41      & 46,988.12      \\
    \hline
    40        & 1w      & 5,086.88       & 4,976.05       \\
              & 2w      & 9,896.65       & 9,736.12       \\
              & 4w      & 16,326.54      & 18,695.84      \\
              & 8w      & 19,183.37      & 37,302.60      \\
    \hline  
    \end{tabular}
\end{table}

\begin{table}[]
    \begin{tabular}{lllllll}
              &               &               & \multicolumn{2}{l}{5 Populations} & \multicolumn{2}{l}{10 Populations} \\
    Dimension & \multicolumn{2}{l}{Increment} & Speedup         & p-value         & Speedup          & p-value         \\
    2         & 1w            & 2w            & 1.94            & 6E-16           & 1.84             & 2E-16           \\
              & 2w            & 4w            & 1.61            & 2E-15           & 1.83             & 1E-15           \\
              & 4w            & 8w            & 1.24            & 1E-06           & 1.77             & 2E-16           \\
    3         & 1w            & 2w            & 1.93            & 2E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.44            & 8E-15           & 1.71             & 2E-16           \\
              & 4w            & 8w            & 1.14            & 3E-05           & 1.83             & 2E-16           \\
    5         & 1w            & 2w            & 1.91            & 9E-16           & 1.91             & 2E-16           \\
              & 2w            & 4w            & 1.52            & 3E-11           & 1.82             & 2E-16           \\
              & 4w            & 8w            & 1.06            & 5E-03           & 1.77             & 2E-16           \\
    10        & 1w            & 2w            & 1.92            & 3E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.58            & 3E-16           & 1.89             & 2E-16           \\
              & 4w            & 8w            & 1.09            & 1E-03           & 1.78             & 2E-16           \\
    20        & 1w            & 2w            & 1.91            & 2E-16           & 1.89             & 2E-16           \\
              & 2w            & 4w            & 1.64            & 2E-15           & 1.97             & 2E-16           \\
              & 4w            & 8w            & 1.04            & 1E-02           & 1.80             & 2E-16           \\
    40        & 1w            & 2w            & 2.00            & 2E-16           & 1.95             & 2E-16           \\
              & 2w            & 4w            & 1.46            & 1E-09           & 1.95             & 2E-16           \\
              & 4w            & 8w            & 1.07            & 3E-02           & 1.98             & 2E-16          
    \end{tabular}
    \end{table}

\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required, in seconds, to complete an instance of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}
%
%
% \subsection{Experiment 1}
% \label{sec:exp1results}
%
with results summarized in Figure \ref{fig:spworker}.  The
experiment consisted of executing the same benchmark on EvoSwarm twice but
changing the number of populations used in each run. This is mainly
intended as a showcase of the flexibility of the tool presented in
this paper, but we also wanted to test how the number of workers
affected the time needed to reach a solution. Adding more populations
might add more overhead, so this might have a noticeable effect.
The left column in that figure has the
results when using five populations, and the right side shows the results for
ten. In principle the main issue is how to find the right number of
workers for a particular problem, but in general we wanted to check
the communication overhead when the size of the problem increases and
how the presented framework reacted to it. % Added some explanation
% here - JJ
